Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-19 ICML2019/main.tex
Tweak.

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance,
the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\todo{
Do we need the experimental on this formula?
It is proved mathematically by case analysis.
For any $r \in \mathcal{R}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
I think it would be a proposition.
}
%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
%\begin{align*}
%LS(\dataobs)
%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\left|~
%\begin{aligned}
%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
%\end{aligned}
%\right|\\
%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
%\end{align*}

>>>>

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
Thanks to the symmetry and triangle-inequality of the Hellinger
distance, we can simplify the local sensitivity.
\begin{lem}
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\end{lem}
\begin{proof}
For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
By taking the supremum, we conclude the statement of this lemma.
\end{proof}

%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
%\begin{align*}
%LS(\dataobs)
%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\left|~
%\begin{aligned}
%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
%\end{aligned}
%\right|\\
%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
%\end{align*}
